Computing volume via non-uniform rectangular infinitesimals

### 2019-08-16 Cav2D/article-template.tex
fixed prismatoid volume
added a summary

\begin{figure}[htb]
\centering
\includegraphics[width=0.75\textwidth]{prismatoid.pdf}
\caption{Another depiction of the solid $\mathcal{S}$ found in Figure~\ref{fig:prismatoid_solid} which highlights the fact that $\mathcal{S}$ is a prismatoid. We can, therefore, calculate its volume with the prismatoid volume equation: $V_{\mathcal{S}}= \frac{h}{6}(A_1+4A_2+A_3)$.
Note, the area of the two basis of $\mathcal{S}$ are denoted by $A1$ and $A3$, the cross-sectional area of the intersection of $\mathcal{S}$ with a plane midway between the two basis is denoted via $A2$, 
and the height of $\mathcal{S}$ is denoted by $h$. Moreover, also note that the surfaces associated with $A1$, $A2$ and $A3$ are depicted in the above figure using shaded sheets. For $\mathcal{S}$ 
$A1=$, $A2=$, $A3 = $ and $h=$. The volume of $\mathcal{S}$ is, therefore, $25.6$.}
\label{fig:prismatoid}
\end{figure}

@@

@@

\caption{Double integrals for sphere. $c_1 \approx 1.1861407$, $c_2 \approx 1.6861407$, $c_3 \approx 0.6861407$ and $c_4 \approx 1.3507811$. $r_1(x) = \frac{1}{2}[\sqrt{17-4x^2}-1]$,
$r_2(x) = \sqrt{-x^2-x+4}$, $r_3(x) = \sqrt{-x^2-(x-1)+4}$ and $r_4(x) = \frac{1}{2}[\sqrt{21-4x^2}-1]$.} 
\label{tab:table1}
\begin{center}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=0.75\textwidth]{sphere_xy.pdf}
\caption{The $xy$-projection of the solid $\mathcal{S}$ depicted in Figure~\ref{fig:sphere_solid} onto the $xy$-plane.}
\label{fig:sphere_xy}
\end{figure}

@@

\begin{abstract}
We presented a novel geometric interpretation of the Riemann-Liouville fractional integral. We found that a Riemann-Liouville integral can 
be thought of as the area obtained by summing together the area of an infinite number of non-rectangular infinitesimals whose shape is determined by the 
order of integration $\alpha$ and the integration limit $t$. We also showed that this geometric interpretation offers many pedagogical benefits as it is very similar
in nature to the geometric interpretation of the Riemann integral.   
\end{abstract}

>>>>

\begin{figure}[htb]
\centering
\includegraphics[width=0.75\textwidth]{prismatoid.pdf}
\caption{Another depiction of the solid $\mathcal{S}$ found in Figure~\ref{fig:prismatoid_solid} which highlights the fact that $\mathcal{S}$ is a prismatoid. We can, therefore, calculate its volume with the prismatoid volume equation: $V_{\mathcal{S}}= \frac{h}{6}(A_1+4A_2+A_3)$.
Note, the area of the two basis of $\mathcal{S}$ are denoted by $A1$ and $A3$, the cross-sectional area of the intersection of $\mathcal{S}$ with a plane midway between the two basis is denoted via $A2$, 
and the height of $\mathcal{S}$ is denoted by $h$. Moreover, also note that the surfaces associated with $A1$, $A2$ and $A3$ are depicted in the above figure using shaded sheets. For $\mathcal{S}$ 
$A1=10.7331$, $A2= 7.1554$, $A3 = 3.5777$ and $h = 3.5777$. The volume of $\mathcal{S}$ is, therefore, $25.6$.}
\label{fig:prismatoid}
\end{figure}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=0.75\textwidth]{sphere_xy.pdf}
\caption{The projection of the solid $\mathcal{S}$ depicted in Figure~\ref{fig:sphere_solid} onto the $xy$-plane.}
\label{fig:sphere_xy}
\end{figure}

@@

\caption{Computing the volume of the solid $\mathcal{S}$ depicted in Figure~\ref{fig:sphere_solid} using a more traditional approach. The region $R_k$ is bounded by $x=a$, $x=b$, $g_1(x)$ and $g_2(x)$. Moreover, $c_1 \approx 1.1861407$, $c_2 \approx 1.6861407$, $c_3 \approx 0.6861407$ and $c_4 \approx 1.3507811$. $r_1(x) = \frac{1}{2}[\sqrt{17-4x^2}-1]$,
$r_2(x) = \sqrt{-x^2-x+4}$, $r_3(x) = \sqrt{-x^2-(x-1)+4}$ and $r_4(x) = \frac{1}{2}[\sqrt{21-4x^2}-1]$. If we sum the last column we obtain the volume of $\mathcal{S}$ which is $0.864043$.} 
\label{tab:table1}
\begin{center}

@@

@@

\begin{abstract}
In this paper we extended the Cavalieri integral into three dimensional euclidean space, i.e. we defined the double Cavalieri integral. 
We also showed that this integral can be used to compute the volume of solids that can be decomposed into an infinite number of 
non-uniform rectangular infinitesimals. We end the paper with two fully worked out examples. In the first example we compute the 
volume of a prismatoid using the double Cavalieri integral. In the second example we compute the volume of a complex solid which is housed within a sphere using the double Cavalieri integral.
\end{abstract}
